Stochastic blockmodels for relational events

### 2012-03-14 docs/slides/slides.tex
Synthetic prediction experiment good (again).  Whole pipeline working.

\vspace{-.8cm}
\begin{align*}
\uncover<5->{
\mbox{Mixing rates} & & \boldsymbol{\eta} =& \left[
\begin {array}{cc}
 \eta_{11}& \eta_{12} \\
 \eta_{21}& \eta_{22} 
\end {array}
\right]
= \left[
\begin {array}{cc}
.8 & .2\\.2 & .8
\end {array}
\right] \\
}
\uncover<6->{
\mbox{Dyad (i,j)} &  & y_{ij} \sim& F(\eta_{z_i,z_j}) \\
}
\uncover<7->{
\mbox{Actor i's class} & & z_i \sim& \mbox{Categorical}(\pi)
}
\end{align*}

@@

@@

\uncover<3>{
\vspace{-3cm}
Benefits:  
\begin{itemize}
\item Adjust for unobserved heterogeneity.
\item Obtain clusters of nodes who have similar interaction dynamic with other parts of the network.
\end{itemize}

}

@@

\begin{frame}{Model specification for $X_{ij}(t)$}
\textbf{Participation shifts} adjust for the next event
\begin{itemize}
\item AB-BA
\item AB-BY
\item AB-AY
\item AB-XA
\item AB-XB
\end{itemize}

@@

\begin{frame}{Synthetic example: $\beta$ and observed counts}
\begin{picture}(0.0,0.0)
   \put(-.1,-0.25){\includegraphics[width=0.7\textwidth]{../../figs/synthetic/params-true}}
   \put(.6,-0.3){\includegraphics[width=0.5\textwidth]{../../figs/synthetic/counts}}
\end{picture}
\end{frame}

\begin{frame}{Synthetic example: slice sampling for $\hat{\beta}$ and Gibbs on
    $\mathbf{z}$}
\begin{picture}(0.0,0.0)
   \put(-.1,-0.25){\includegraphics[width=0.7\textwidth]{../../figs/synthetic/params-estimates}}
   \put(.6,-0.3){\includegraphics[width=0.5\textwidth]{../../figs/synthetic/counts}}
\end{picture}

>>>>

\vspace{-.8cm}
\begin{align*}
\uncover<5->{
\mbox{Mixing rates} & & \boldsymbol{\eta} =& \left[
\begin {array}{cc}
 \eta_{11}& \eta_{12} \\
 \eta_{21}& \eta_{22} 
\end {array}
\right]
= \left[
\begin {array}{cc}
.8 & .2\\.2 & .8
\end {array}
\right] \\
}
\uncover<6->{
\mbox{Actor i's class} & & z_i \sim& \mbox{Categorical}(\pi) \\
}
\uncover<7->{
\mbox{Dyad (i,j)} &  & y_{ij} \sim& F(\eta_{z_i,z_j}) \\
}
\end{align*}

@@

\begin{frame}{Stochastic blockmodels for relational event data}
Subsets of interactions may have distinct dynamics
\begin{itemize}
  \item Core-periphery structures \\(e.g. periphery only sends, core reciprocates immediately)
  \item<2-> Cohesive subgroups with differing behavior \\(e.g. students and professors)
  \end{itemize}
\end{frame}

@@

\uncover<3>{
\vspace{-3cm}
Benefits:  
\begin{itemize}
\item Adjust for unobserved heterogeneity.
\item Obtain clusters of nodes who have similar interaction dynamic with other parts of the network.
\end{itemize}
}

@@

\begin{frame}{Model specification for $\mathbf{s}(t,i,j)$}
\textbf{Participation shifts} adjust for the next event
\begin{itemize}
\item AB-BA
\item AB-BY
\item AB-AY
\item AB-XA
\item AB-XB
\end{itemize}

@@

\begin{frame}{Synthetic example: $\beta$ and observed counts}
\begin{picture}(0.0,0.0)
   \put(-.1,-0.25){\includegraphics[width=0.7\textwidth]{../../figs/synthetic/params-true}}
   \put(.55,-0.25){\includegraphics[width=0.55\textwidth]{../../figs/synthetic/counts}}
\end{picture}
\end{frame}

\begin{frame}{Synthetic example: slice sampling for $\beta$ and Gibbs on
    $\mathbf{z}$}
\begin{picture}(0.0,0.0)
   \put(-.1,-0.25){\includegraphics[width=0.7\textwidth]{../../figs/synthetic/params-estimates}}
   \put(.65,-0.25){\includegraphics[width=0.55\textwidth]{../../figs/synthetic/counts}}
\end{picture}
